\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-09 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results
add references, minor changes in the Numerical simulation section

\begin{figure}
\centering
\includegraphics[width=\linewidth]{IEEE14BusWithUnc.pdf}
\caption{\small{A schematic of the IEEE 14 bus test system with stochastic uncertainties. The Uncertainty sources may include stochastic forcing and parametric uncertainties at some generators, random variabilities at some loads, and parametric uncertainties along some transmission lines. For depiction purposes, we indicated the parametric uncertainties as PDFs, and stochastic forcing as intermittent signals.}}
\label{fig:Motivating}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{UncPropBlockDiagm.pdf}
\caption{\small{Block diagram for joint state PDF propagation.}}
\label{fig:UncertaintyPropagation}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=.8\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed proximal algorithm for propagating the joint state PDF as probability weighted scattered point cloud $\{\tilde{\bm{x}}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$. The states $\{\tilde{\bm{x}}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ are updated via discrete version of the proximal recursion (\ref{KineticProx}) as detailed in Sec. \ref{sec:ProxAlgo}.}}
\label{fig:BlockDiagm}
\end{figure}

@@

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
Following Sec. \ref{subsec:samplepathdynamics}, we consider the Kron-reduced dynamics \eqref{ItoSDEcomponentlevel} for the IEEE 14 bus system shown in Fig. \ref{fig:Motivating}. In this case, we have $n=5$ nodes which correspond to the buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. {\red{The parameter values in \eqref{DefParam} use the network reduced admittance matrix computed from the CITE?? The parameters $m_{i}, \gamma_{i}$ are obtained from ....}} We randomly generated $\sigma_{i}\in [1,5]$ as
\[(\sigma_{1},\hdots,\sigma_5) = \left(2.4628, 4.9266, 4.8724, 1.4215, 3.8681\right).\]

@@

The mean angles \eqref{MeanAngleInitialIEEE14} were obtained as steady state power flow solutions {\red{for the generator phase angles with constant load?? Please complete/edit this sentence}} Larger $\kappa_{i}$ entails a higher concentration around the mean angle $\mu_{\theta_{i}}(0)$ (setting $\kappa_i=0$ implies that $\theta_{i}(0)$ follows uniform distribution over $[0,2\pi)$).

@@

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Parameter description & Values\\
\hline\hline
&\\
nominal frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0,0.25]\right)& \text{for}\; i\neq j
\end{cases}$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0.7,1.2]\right) & \text{for}\; i\neq j	
\end{cases}$\\
& \\
\hline
\end{tabular}
\caption{Parameters used for the numerical simulation in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$ where the number of generators $n=50$ in Sec. \ref{subsec:NumSimSynthetic}.}
\label{table:ParamUncertaintiesSynthetic}
\end{table}

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{IEEE14BusWithUnc.pdf}
\caption{\small{A schematic of the IEEE 14 bus test system with stochastic uncertainties. The Uncertainty sources may include stochastic forcing and parametric uncertainties at some generators, random variabilities at some loads, and parametric uncertainties along some transmission lines. For depiction purposes, we indicated the parametric uncertainties as PDFs, and stochastic forcing as intermittent signals.}}
\label{fig:Motivating}
\vspace*{-0.1in}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{UncPropBlockDiagm.pdf}
\caption{\small{Block diagram for joint state PDF propagation.}}
\label{fig:UncertaintyPropagation}
\vspace*{-0.1in}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=.7\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed proximal algorithm for propagating the joint state PDF as probability weighted scattered point cloud $\{\tilde{\bm{x}}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$. The states $\{\tilde{\bm{x}}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ are updated via discrete version of the proximal recursion (\ref{KineticProx}) as detailed in Sec. \ref{sec:ProxAlgo}.}}
\label{fig:BlockDiagm}
\vspace*{-0.1in}
\end{figure}

@@

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
Following Sec. \ref{subsec:samplepathdynamics}, we consider the Kron-reduced dynamics \eqref{ItoSDEcomponentlevel} for the IEEE 14 bus system shown in Fig. \ref{fig:Motivating}. In this case, we have $n=5$ nodes which correspond to the buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}.
{\red{The original parameters of the 14-bus system are from Matpower \cite{zimmerman2010matpower}. The calculation of network reduced admittance matrices in \eqref{DefParam} is described in \ref{subsec:samplepathdynamics} and \cite{dorfler2012kron}.
The parameters $m_{i}, \gamma_{i}$ are obtained from ANDES \cite{cui2021andes}.}}
We randomly generated $\sigma_{i}\in [1,5]$ as
\[(\sigma_{1},\hdots,\sigma_5) = \left(2.4628, 4.9266, 4.8724, 1.4215, 3.8681\right).\]

@@

The mean angles \eqref{MeanAngleInitialIEEE14} were obtained from steady state AC power flow solutions. Larger $\kappa_{i}$ entails a higher concentration around the mean angle $\mu_{\theta_{i}}(0)$ (setting $\kappa_i=0$ implies that $\theta_{i}(0)$ follows uniform distribution over $[0,2\pi)$).

@@

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Parameter description & Values\\
\hline\hline
&\\
nominal frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0,0.25]\right)& \text{for}\; i\neq j
\end{cases}$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0.7,1.2]\right) & \text{for}\; i\neq j	
\end{cases}$\\
& \\
\hline
\end{tabular}
\caption{Parameters used for the numerical simulation in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$ where the number of generators $n=50$ in Sec. \ref{subsec:NumSimSynthetic}.}
\label{table:ParamUncertaintiesSynthetic}
\vspace*{-0.1in}
\end{table}

@@

\bibitem{zimmerman2010matpower}
R.D.~Zimmerman, C.E.~Murillo-S{\'a}nchez, R.J. Thomas, ``MATPOWER: Steady-state operations, planning, and analysis tools for power systems research and education'', \emph{IEEE Transactions on power systems},  Vol. 26, No. 1, pp. 12--19, 2010.

\bibitem{cui2021andes}
H.~Cui, F.~Li and K.~Tomsovic, ``Hybrid Symbolic-Numeric Framework for Power System Modeling and Analysis,'' \emph{IEEE Transactions on Power Systems}, vol. 36, no. 2, pp. 1373-1384, 2021.
